\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Liouville'S CONSTANT}
\author{Venkata Sai Parthasarathi Hemanth }
\date{Interviewer:Venkata Sai Parthasarathi Hemanth}
\title{INTERVIEW DETAILS}
\author{Interviewer:Venkata Sai Parthasarathi Hemanth}
\author{Interviewee:Vedant Saini}

\begin{document}

\maketitle
\begin{itemize}
\item
Interviewer: Do you have any idea about Liouville’s constant?\newline
Interviewee: it is a constant represented as 
$L=\sum_{n=1}^{\infty} 10^{-n!}$.\newline
\item
Interviewer: Are there any uses of this constant practically?\newline
Interviewee: I know that by establishing that a given number is a Liouville number, it provides a useful tool for proving a given number is transcendental. \newline
\item
Interviewer: Is there anything interesting to know about this number?\newline
Interviewee: Yes. The number was the first ever decimal constant to be proven transcendental.\newline
\item
Interviewer: How frequently is this constant used in daily life? \newline
Interviewee: This is not used frequently in everyday scenarios.\newline
\item
Interviewer: What would you like the calculator size to be?\newline
Interviewee: I would like if the calculator could fit in my palm so that it is easy to hold.\newline
\item
Interviewer: Would you prefer having the basic operators at the same place or at random places?\newline
Interviewee: Since these operators are frequently used in calculations, I would want these operators to be in the same place. \newline
\item
 Interviewer: What additional button/buttons would you prefer in the calculator?\newline
 Interviewee: It would be helpful if there is a history button so that I can track the operations made.\newline


\end{itemize}

\end{document}